Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-04 draft/accordionComplexSurfaces.tex
Fixed referenced Thm 4.22.
comments to do

Possible titles, depending on what we want to insist on:
\begin{enumerate}
\item Accordion / slalom / non-kissing / support $\tau$-tilting complexes all coincide for gentle algebras
\item Non-kissing and non-crossing complexes for gentle algebras
\item Combinatorial models for support $\tau$-tilting on gentle algebras: accordion, slalom and non-kissing complexes
\end{enumerate}

@@

Algebras and dissections have lived together before... (mention clusters)

@@

@@

\begin{proof}
\yann{I have to merge two cases}
Let~$\alpha$ be a~$\dissection$-accordion.
Let~$\beta$,~$\gamma$,~$\delta$ be three consecutive arcs of~$\dissection$ crossed by~$\gamma$.
Let~$m\in\dissection$ be the common endpoint of~$\beta$ and $\gamma$ given by Definition~\ref{def:accordion} and let~$n\in\dissection$ be the common endpoint of~$\gamma$ and~$\delta$.
If $m=n$, then the segment of~$\alpha$ between~$\beta$ and~$\delta$ stays in the same face of~$\dissection\dual$.
Otherwise, when crossing~$\gamma$, the accordion~$\alpha$ leaves the face~$m\dual$ of $\dissection\dual$ and enters the face~$n\dual$.
In the surface obtained by glueing the two cells~$m\dual$ and~$n\dual$ along~$\gamma\dual$, the marked points~$m$ and~$n$ are separated by~$\alpha$.
Conversely, assume that~$\alpha$ is an arc of~$(\surface, B)$ which is not a $\dissection$-accordion.
We are in one of the following cases.

@@

Case 4: If~$\alpha$ stays inside a blue cell, then it rolls around a~$\dissection\dual$ puncture.
There is a~$\dissection\dual$-arc~$\beta$ ending in that puncture. When~$\alpha$ crosses~$\beta$, the puncture stays on the same side of~$\alpha$, hence~$\alpha$ is not a~$\dissection\dual$-slalom.
\end{proof}

@@

@@

We now associate a surface to a locally gentle bound quiver.

@@

\begin{theorem}
\label{thm:bijectionLocallyGentleAndSurfaces}
 Up to isomorphism, the constructions of Definitions \ref{def:quiverDualDissections} and \ref{def:surfaceQuiver} are inverse to each other.
 They induce a bijection between the set of isomorphism classes of locally gentle algebras and the set of homeomorphism classes of marked surfaces with a pair of dual cellular dissections.
\end{theorem}
\pierreguy{How much detail for a proof? Or is it clear?}

@@

@@

\begin{lemma}
\label{lemm:curveOfAWalkIsAccordion}
Let~$\omega$ be a walk on~$\bar Q$.  Then~$\curveof(\omega)$ is a~$\dissection_{\bar Q}$-accordion.
\end{lemma}
\begin{proof}
 This is because~$\curveof(\omega)$ follows angles in~$\dissection_{\bar Q}$ by definition.
\end{proof}

\begin{lemma}
\label{lemm:accordionsAreCurvesOfWalks}
Let~$\gamma$ be a~$\dissection_{\bar Q}$-accordion.  There exists a unique undirected walk~$\walk(\gamma)$ such that we have~$\curveof(\walk(\gamma)) = \gamma$.
\end{lemma}
\begin{proof}
 \pierreguy{TO DO}
\end{proof}

@@

\begin{lemma}
\label{lem:nonKissing=nonCrossing}
Let~$\omega_1$ and~$\omega_2$ be walks on~$\bar Q$.  Then~$\omega_1$ and~$\omega_2$ are non-kissing if and only if the~$\dissection_{\bar Q}$-accordions~$\curveof(\omega_1)$ and~$\curveof(\omega_2)$ are non-crossing on~$\surface(\bar Q)$.
\end{lemma}
\begin{proof}
 \pierreguy{Picture No.4}
\end{proof}

\begin{theorem}
\label{thm:complexesCoincide}
\begin{itemize}
\item For any locally gentle bound quiver~$\bar Q$, the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$, therefore to the accordion complex~$\AC[\dissection_{\bar Q}]$ and to the slalom complex~$\SC[{\dissection_{\bar Q}}\dual]$.
\item For any pair of dual cellular dissections~$\dissection, \dissection\dual$ of an oriented surface, the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection, \dissection\dual}]$.
\end{itemize}
\end{theorem}
\begin{proof}
 The first point is a consequence of Proposition \ref{prop:walks=arcs}, Lemma \ref{lem:nonKissing=nonCrossing} and Proposition \ref{prop:accordionsSlaloms}.
 The second point is a consequence of Theorem \ref{thm:bijectionLocallyGentleAndSurfaces} and of the first point.
\end{proof}

@@

\begin{definition}
For any arrow~$\alpha \in Q\blossom_1$ and any two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at an occurrence of~$\alpha^\pm$,
let~$\sigma$ denote their maximal common substring containing that occurrence of~$\alpha$.
Since~$\mu_\star \ne \nu_\star$, this common substring~$\sigma$ is strict, so~$\mu_\star$ and~$\nu_\star$ split at one endpoint of~$\sigma$.
The \defn{countercurrent order at~$\alpha$} is defined by~$\mu_\star \prec_\alpha \nu_\star$ when~$\mu_\star$ enters and/or exits~$\sigma$ in the direction pointed by~$\alpha$, while~$\nu_\star$ enters and/or exits~$\sigma$ in the direction opposite to~$\alpha$.
\end{definition}
\pierreguy{Add a picture here?}

\begin{remark}
\label{rema:countercurrentOrderOnSurface}
Using Theorem \ref{thm:complexesCoincide}, we can translate the definition of the countercurrent order~$\prec_\alpha$ to the language of~$\dissection$-accordions.
An arrow~$\alpha$ in~$\bar Q\blossom$ corresponds to an angle at a point $v$ between two arcs of~$\dissection$.
Two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at~$\alpha$ in~$\bar Q$ correspond to two distinct non-crossing~$\dissection$-accordions~$\gamma$ and~$\delta$ passing in front of this angle.
Then~$\gamma \prec_\alpha \delta$ if~$\gamma$ passes closer to~$v$ than~$\delta$ does.
\pierreguy{Should we prove this?}
%
\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=1]{orderCurves}}
	\caption{The order~$\prec_\alpha$ on marked walks is the order in which the corresponding curves cross the angle corresponding to~$\alpha$.}
	\label{fig:orderCurves}
\end{figure}
\end{remark}

@@

The following definition from \cite[Definition 2.23]{PaluPilaudPlamondon} extends to the setting locally gentle algebras.

@@

\begin{proposition}
\label{prop:numberOfDistinguishedArrows}
Let~$F$ be a facet of~$\NKC$.
\begin{itemize}
 \item Each bending walk of~$F$ has exactly two distinguished arrows.
 \item Each finite straight walk of~$F$ has exactly one distinguished arrows.
 \item Each infinite straight walk of~$F$ has exactly zero distinguished arrows.
\end{itemize}
\end{proposition}
\begin{proof}
 \pierreguy{Vincent has the proof of this proposition.}
 The first two dots in this proposition are proven in Lemma~\ref{lem:ExistenceOfDistinguishedArrows}.
\end{proof}

@@

{\it Proof of Proposition \ref{prop:purity}.}
\pierreguy{TO DO}

@@

>>>>

\yann{Abstract to do.}

@@

Algebras and dissections have lived together before... (mention clusters)
\pierreguy{Finish introduction.}

@@

\vincent{Connection.}

@@

\begin{proof}
\vincent{Careful: arcs / curves.}
Let~$\alpha$ be a~$\dissection$-accordion.
Let~$\beta$,~$\gamma$,~$\delta$ be three consecutive arcs of~$\dissection$ crossed by~$\gamma$.
Let~$m\in\dissection$ be the common endpoint of~$\beta$ and $\gamma$ given by Definition~\ref{def:accordion} and let~$n\in\dissection$ be the common endpoint of~$\gamma$ and~$\delta$.
If $m=n$, then the segment of~$\alpha$ between~$\beta$ and~$\delta$ stays in the same face of~$\dissection\dual$.
Otherwise, when crossing~$\gamma$, the accordion~$\alpha$ leaves the face~$m\dual$ of $\dissection\dual$ and enters the face~$n\dual$.
In the surface obtained by glueing the two cells~$m\dual$ and~$n\dual$ along~$\gamma\dual$, the marked points~$m$ and~$n$ are separated by~$\alpha$.
Conversely, assume that~$\alpha$ is an arc of~$(\surface, B)$ which is not a $\dissection$-accordion.
We are in one of the following cases.

@@

Case 4: If~$\alpha$ stays inside a $\dissection$-cell, then it rolls around a~$\dissection\dual$ puncture.
There is a~$\dissection\dual$-arc~$\beta$ ending in that puncture. When~$\alpha$ crosses~$\beta$, the puncture stays on the same side of~$\alpha$, hence~$\alpha$ is not a~$\dissection\dual$-slalom.
\end{proof}

@@

\pierreguy{reference OPS}

@@

We now associate a surface to a locally gentle bound quiver.
\pierreguy{reference OPS}

@@

\vincent{Connection.}

\begin{theorem}
\label{thm:bijectionLocallyGentleAndSurfaces}
 Up to isomorphism, the constructions of Definitions \ref{def:quiverDualDissections} and \ref{def:surfaceQuiver} are inverse to each other.
 They induce a bijection between the set of isomorphism classes of locally gentle algebras and the set of homeomorphism classes of marked surfaces with a pair of dual cellular dissections.
\end{theorem}

@@

\vincent{TODO: surfaces double cycles.}
\end{example}

\pierreguy{Remark on the comparison with the surface of OPS}

@@

\begin{lemma}
\label{lemm:curveOfAWalkIsAccordion}
Let~$\omega$ be a walk on~$\bar Q$.  Then~$\curveof(\omega)$ is a~$\dissection_{\bar Q}$-accordion.
\end{lemma}

\begin{proof}
This is because~$\curveof(\omega)$ follows angles in~$\dissection_{\bar Q}$ by definition.
\end{proof}

\begin{lemma}
\label{lemm:accordionsAreCurvesOfWalks}
Let~$\gamma$ be a~$\dissection_{\bar Q}$-accordion.  There exists a unique undirected walk~$\walk(\gamma)$ such that we have~$\curveof(\walk(\gamma)) = \gamma$.
\end{lemma}
\begin{proof}
 \pierreguy{TO DO}
 \vincent{figure}
\end{proof}

@@

\begin{lemma}
\label{lem:nonKissing=nonCrossing}
Let~$\omega_1$ and~$\omega_2$ be walks on~$\bar Q$.  Then~$\omega_1$ and~$\omega_2$ are non-kissing if and only if the~$\dissection_{\bar Q}$-accordions~$\curveof(\omega_1)$ and~$\curveof(\omega_2)$ are non-crossing on~$\surface(\bar Q)$.
\end{lemma}

\begin{proof}
 \pierreguy{Picture No.4}
 \vincent{figure}
\end{proof}

\begin{theorem}
\label{thm:complexesCoincide}
\begin{itemize}
\item For any locally gentle bound quiver~$\bar Q$, the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$, therefore to the accordion complex~$\AC[\dissection_{\bar Q}]$ and to the slalom complex~$\SC[{\dissection_{\bar Q}}\dual]$.
\item For any pair of dual cellular dissections~$\dissection, \dissection\dual$ of an oriented surface, the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection, \dissection\dual}]$.
\end{itemize}
\end{theorem}

\begin{proof}
 The first point is a consequence of Proposition \ref{prop:walks=arcs}, Lemma \ref{lem:nonKissing=nonCrossing} and Proposition \ref{prop:accordionsSlaloms}.
 The second point is a consequence of Theorem \ref{thm:bijectionLocallyGentleAndSurfaces} and of the first point.
\end{proof}

@@

The following definition is illustrated in \fref{fig:orderCurves}.

\begin{definition}
For any arrow~$\alpha \in Q\blossom_1$ and any two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at an occurrence of~$\alpha^\pm$,
let~$\sigma$ denote their maximal common substring containing that occurrence of~$\alpha$.
Since~$\mu_\star \ne \nu_\star$, this common substring~$\sigma$ is strict, so~$\mu_\star$ and~$\nu_\star$ split at one endpoint of~$\sigma$.
The \defn{countercurrent order at~$\alpha$} is defined by~$\mu_\star \prec_\alpha \nu_\star$ when~$\mu_\star$ enters and/or exits~$\sigma$ in the direction pointed by~$\alpha$, while~$\nu_\star$ enters and/or exits~$\sigma$ in the direction opposite to~$\alpha$.
\end{definition}

\begin{remark}
\label{rema:countercurrentOrderOnSurface}
Using Theorem \ref{thm:complexesCoincide}, we can translate the definition of the countercurrent order~$\prec_\alpha$ to the language of~$\dissection$-accordions.
An arrow~$\alpha$ in~$\bar Q\blossom$ corresponds to an angle at a point $v$ between two arcs of~$\dissection$.
Two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at~$\alpha$ in~$\bar Q$ correspond to two distinct non-crossing~$\dissection$-accordions~$\gamma$ and~$\delta$ passing in front of this angle.
Then~$\gamma \prec_\alpha \delta$ if~$\gamma$ passes closer to~$v$ than~$\delta$ does.
%
\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=1]{orderCurves}}
	\caption{The order~$\mu \prec_\alpha \nu$ on marked walks is the order in which the corresponding curves~$\curveof(\mu)$ and~$\curveof(\nu)$ cross the angle corresponding to~$\alpha$.}
	\label{fig:orderCurves}
\end{figure}
\end{remark}

@@

The following definition from \cite[Definition 2.23]{PaluPilaudPlamondon} extends to the setting of locally gentle algebras.

@@

\begin{proposition}
\label{prop:numberOfDistinguishedArrows}
Let~$F$ be a facet of~$\NKC$.
\begin{itemize}
 \item Each bending walk of~$F$ has exactly two distinguished arrows.
 \item Each finite straight walk of~$F$ has exactly one distinguished arrows.
 \item Each infinite straight walk of~$F$ has exactly zero distinguished arrows.
\end{itemize}
\end{proposition}
\begin{proof}
 \vincent{Vincent has the proof of this proposition.}
 The first two dots in this proposition are proven in Lemma~\ref{lem:ExistenceOfDistinguishedArrows}.
\end{proof}

@@

\begin{proof}[Proof of Proposition \ref{prop:purity}.]
\vincent{TO DO}
\end{proof}

@@

\section{$\b{g}$-, $\b{c}$- and $\b{d}$-vectors}

\vincent{To do on the walks, on the accordions and on the slaloms.}
